Non-linear Spatio-temporal modelling using the Integro-Difference Equation

### 2010-07-08 ltx/second_order_framework/second_order_manuscript.tex
completed discritization

@@

>>>>

\begin{equation}\label{eq:SecondOrderEulerMaruyamaDis}

@@

where $T_s$ is the time step, the increments $W_{t+T_s}(\mathbf r)-W_t(\mathbf r)$ is normally distributed with mean zero and covariance function $T_s\gamma(\mathbf r-\mathbf r')$. We rewrite \eqref{eq:SecondOrderEulerMaruyamaDis} as
 \begin{bmatrix} v_{t+T_s}(\mathbf r) \\ \tilde{v}_{t+T_s}(\mathbf r)\end{bmatrix}=\begin{bmatrix}1 & T_s \\ -\zeta^2 T_s & 1-2\zeta T_s \end{bmatrix}\begin{bmatrix} v_t(\mathbf r)\\ \tilde{v}_t(\mathbf r)\end{bmatrix}+T_s\begin{bmatrix}0 \\ g'(\mathbf r, t)\end{bmatrix}+\begin{bmatrix}0 \\ 1 \end{bmatrix}e_t(\mathbf r)
 where $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf 0,T_s\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $T_s\gamma(\mathbf{r}-\mathbf{r}')$. To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper. 
